Kindly Bent To Free Us

### 2020-08-03 kindly/slides-icfp.tex
Cleanup the "everything" slide.

% \begin{onlyenv}<2>
% \begin{minted}[texcomments=true]{OCaml}
% let gradeDB = ... in
% let avg =
%  let grade topic = Dbm.find &gradeDB topic in (* \Y Capture *)
%  (grade "math" + grade "compsci") / 2
% in
% Dbm.add &!gradeDB "average" avg (* \Y Exclusive borrow *)
% \end{minted}
% \end{onlyenv}
\begin{onlyenv}<1>
  \textbf{Rule 1}: Cannot use a borrow and the thing itself simultaneously
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
f (gradeDB, &gradeDB) (* \N Conflicting use and borrow! *)
\end{minted}
\end{onlyenv}%
\begin{onlyenv}<2>
  \textbf{Rule 2}: Cannot use an exclusive borrow and any other borrow simultaneously
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
f (&!gradeDB, &gradeDB) (* \N Conflicting borrows! *)
\end{minted}
\end{onlyenv}%
\begin{onlyenv}<3->
  \textbf{Rule 3}: Borrows must not escape
  \begin{onlyenv}<3>
\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let f () = 
  let gradeDB = ... in
  #\tikzcoord{R1}#let x = (&gradeDb, "mygrades") in#\tikzcoord{R2}#
  #\tikzcoord{R3}#x#\tikzcoord{R4}#
  (* \N Borrow escaping its scope! *)
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<4>
\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let f () = 
  let gradeDB = ... in
  #\tikzcoord{R1}#{| let x = (&gradeDb, "mygrades") in#\tikzcoord{R2}#
  #\tikzcoord{R3}#x |}#\tikzcoord{R4}#
  (* \N Borrow escaping its scope! *)
\end{minted}
  \end{onlyenv}
  \begin{tikzpicture}[remember picture,overlay]%
    \begin{onlyenv}<4>
      \node[code,rounded corners=0,color=green,fit=(R1) (R2)] {};
      \node[code,rounded corners=0,minimum height=15pt,yshift=1pt,color=green,fit=(R3) (R4)] {};
    \end{onlyenv}
  \end{tikzpicture}%
\end{onlyenv}%
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Everything together}
  \TODO{Make that straighter/punchier}

  \begin{onlyenv}<1>
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
(Dbm.find &gradeDB "math" + Dbm.find &gradeDB "compsci") / 2
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<2>
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
let grade subject = Dbm.find &gradeDB subject in (* \Y Capture *)
(grade "math" + grade "compsci") / 2
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<3>
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
let grade = Dbm.find &gradeDB in (* \Y Partial application *)
(grade "math" + grade "compsci") / 2
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<4->
\begin{minted}[texcomments=true]{OCaml}
(* \Y Easy functional abstraction *)
let average db subjects = 
  List.map (Dbm.find db) subjects / List.length subjects

let main () =
  let gradeDB = ... in
  let avg = average &gradeDB ["math";"compsci";...] in
  Dbm.add &!gradeDB "average" avg
\end{minted}
  \end{onlyenv}
\end{frame}

>>>>

% \begin{onlyenv}<2>
% \begin{minted}[texcomments=true]{OCaml}
% let gradeDB = ... in
% let avg =
%  let grade topic = Dbm.find &gradeDB topic in (* \Y Capture *)
%  (grade "math" + grade "compsci") / 2
% in
% Dbm.add &!gradeDB "average" avg (* \Y Exclusive borrow *)
% \end{minted}
% \end{onlyenv}
\begin{onlyenv}<1>
  \textbf{Rule 1}: Cannot use a borrow and the thing itself simultaneously
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
f (gradeDB, &gradeDB) (* \N Conflicting use and borrow! *)
\end{minted}
\end{onlyenv}%
\begin{onlyenv}<2>
  \textbf{Rule 2}: Cannot use an exclusive borrow and any other borrow simultaneously
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
f (&!gradeDB, &gradeDB) (* \N Conflicting borrows! *)
\end{minted}
\end{onlyenv}%
\begin{onlyenv}<3->
  \textbf{Rule 3}: Borrows must not escape
  \begin{onlyenv}<3>
\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let f () = 
  let gradeDB = ... in
  #\tikzcoord{R1}#let x = (&gradeDb, "mygrades") in#\tikzcoord{R2}#
  #\tikzcoord{R3}#x#\tikzcoord{R4}#
  (* \N Borrow escaping its scope! *)
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<4>
\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let f () = 
  let gradeDB = ... in
  #\tikzcoord{R1}#{| let x = (&gradeDb, "mygrades") in#\tikzcoord{R2}#
  #\tikzcoord{R3}#x |}#\tikzcoord{R4}#
  (* \N Borrow escaping its scope! *)
\end{minted}
  \end{onlyenv}
  \begin{tikzpicture}[remember picture,overlay]%
    \begin{onlyenv}<4>
      \node[code,rounded corners=0,color=red,fit=(R1) (R2)] {};
      \node[code,rounded corners=0,minimum height=15pt,yshift=1pt,color=red,fit=(R3) (R4)] {};
    \end{onlyenv}
  \end{tikzpicture}%
\end{onlyenv}%
\end{frame}

@@

  % \begin{tikzpicture}[remember picture,overlay]
  %   \begin{onlyenv}<2->
  %     \node[code,color=yellow,fit=(A1) (A2)] {};
  %     \node[code,color=red,fit=(U1) (U2)] {};
  %     \node[code,color=red,fit=(U3) (U4)] {};
  %   \end{onlyenv}
  %   \node[code,color=yellow,fit=(AX1) (AX2)] {};
  %   \node[code,color=red,fit=(UX1) (UX2)] {};
  % \end{tikzpicture}

\begin{frame}[fragile]
  \frametitle{Everything together}

  \begin{onlyenv}<1>
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
let avg =
  (Dbm.find &gradeDB "math" + Dbm.find &gradeDB "compsci") / 2

in
Dbm.add &!gradeDB "average" avg
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<2>
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
let avg =
  let grade subject = Dbm.find &gradeDB subject in (* \Y Capture *)
  (grade "math" + grade "compsci") / 2
in
Dbm.add &!gradeDB "average" avg
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<3>
\begin{minted}[texcomments=true]{OCaml}
let gradeDB = ... in
let avg =
  let grade = Dbm.find &gradeDB in (* \Y Partial application *)
  (grade "math" + grade "compsci") / 2
in
Dbm.add &!gradeDB "average" avg
\end{minted}
  \end{onlyenv}
  \begin{onlyenv}<4->
    \begin{onlyenv}<4>%
\begin{minted}[texcomments=true]{OCaml}
let average db subjects = 
  List.map (Dbm.find db) subjects / List.length subjects

let main () =
  let gradeDB = ... in
  let avg = average &gradeDB ["math";"compsci";...] in
  Dbm.add &!gradeDB "average" avg
\end{minted}
    \end{onlyenv}%
    \begin{onlyenv}<5>%
\begin{minted}[texcomments=true,escapeinside=\#\#]{OCaml}
let average db subjects #\tikzcoord{eq1}#=#\tikzcoord{eq2}#
  List.map (Dbm.find db) subjects / List.length subjects

let main () =
  let gradeDB = ... in
  let avg = #\tikzcoord{R1}#{| average &gradeDB ["math";"compsci";...] |}#\tikzcoord{R2}# in
  #\tikzcoord{R3}#{| Dbm.add &!gradeDB "average" avg |}#\tikzcoord{R4}#
\end{minted}
    \end{onlyenv}%
  \end{onlyenv}%
  \begin{tikzpicture}[remember picture,overlay]%
    \begin{onlyenv}<5>
      \node[code,fit=(eq1) (eq2)] (eq) {};
      \draw[overlay,link,<-] (eq) to[out=90,in=-90]
      +(0.5,1) node[annot,scale=1.2,anchor=south]
      {No type annotation};
      \node[code,rounded corners=0,color=red,fit=(R1) (R2)] (RA) {};
      \node[code,rounded corners=0,color=yellow,fit=(R3) (R4)] (RB) {};
      \node[annot,scale=1.2] at ($(R4)+(1,-1)$) (AR) {Disjoint regions};
      \draw[link] (AR) to[out=90,in=-40] (RA.-8);
      \draw[link] (AR) to[out=180,in=-40] (RB.-8);
    \end{onlyenv}
  \end{tikzpicture}%
\end{frame}
